### 2019-08-08 paper.tex
Fixed tables, new images HD

\chapterauthor{P\'ia Cort\'es-Zuleta, Patricio Rojo, Songhu Wang, Tobias C. Hinse, Sergio Hoyer, Bastian Sanhueza, Patricio Correa-Amaro, Julio Albornoz}

@@

@@

\begin{table*}
\caption{Log of Observations}             
\label{log_table}      
\centering          
\begin{tabular}{cccccccc}
\hline\hline       
Target & Date & Epoch\footnotemark{a} & Telescope & Filter & N & $t_{exp}$\footnotemark{b} & RMS\footnotemark{c} \\
& (UTC) &       &           &       &                   & (seconds) & (mmag)\\
\hline  
WASP-18 & 2009 Oct 28 &-1904 & SMARTS 1 m & $I$ & 1412 & 1.5 & 8.49  \\
 				& 2009 Oct 29 & -1903 & SMARTS 1 m & $I$ & 1435 & 2 & 5.67 \\
				& 2009 Oct 30 & -1902 & SMARTS 1 m & $I$ & 1198 & 2  & 4.50 \\
 				& 2011 Sep 06 & -1184 & SMARTS 1 m & $I$ & 203 & 15 & 2.40 \\
				& 2016 Sep 24\footnotemark{d} & 776 & Danish 1.54 m & $I$ & 138 & 90 & 1.05  \\
				& 2016 Sep 25\footnotemark{d} & 777 &Danish 1.54 m & $I$ & 159 & 90  & 0.96  \\
			    & 2016 Sep 26\footnotemark{d} & 778 & Danish 1.54 m & $I$ & 113 & 90 & 0.87  \\ \smallskip
				& 2017 Sep 29\footnotemark{d} & 1169 & Danish 1.54 m & $R$ & 330 & 30 & 2.53 \\
WASP-19 & 2011 Apr 22 & -923 & SMARTS 1 m &   $I$ &  626  & 12  & 4.31   \\
     & 2011 Dec 24 & -611 & SMARTS 1 m &   $I$ & 364  & 18  & 35.9 \\
     & 2013 Mar 13 & -47 & Danish 1.54 m & $R$ & 336 & 35 & 2.15\\
     & 2013 Apr 20 & 1 & Danish 1.54 m & $R$ & 153 & 100 & 0.80 \\
     & 2015 Mar 04 & 867 & Danish 1.54 m & $R$ & 235 & 60 & 0.84\\
     & 2016 Apr 14 & 1383 & Danish 1.54 m & $I$ & 87 & 100 & 0.71\\
     & 2017 Feb 14 & 1771 & Danish 1.54 m & $I$ & 137 & 90 & 0.79\\
     & 2017 Apr 08 & 1838 & Danish 1.54 m & $R$ & 125 & 90 & 0.81\\\smallskip
     & 2017 Oct 03 & 2064 & Danish 1.54 m & $R$ & 43 & 110 & 1.70\\ 
 WASP-77 & 2013 Aug 20 & -659 & ETD\footnotemark{e} & $clear$ & 103 & 120 & 3.87  \\
    & 2013 Oct 30 & -606 & ETD\footnotemark{e} & $clear$ & 690 & 12 & 5.91 \\
    & 2015 Sep 29 & -92 & Danish 1.54 m & $R$ &  244 & 30 &  0.84\\
      & 2015 Oct 03 & -89 & Danish 1.54 m & $R$ &  138 & 60 &  1.84\\
      & 2016 Sep 26 & 175 & Danish 1.54 m & $I$ &  90 & 90 &  0.47\\
      & 2016 Sep 30 & 177 & ETD\footnotemark{e}& $clear$ & 66 & 180 & 2.74 \\
      & 2016 Oct 07 & 183 & Warsaw 1.3 m & $I$ & 237 & 60 &  2.38 \\ 
      & 2016 Dec 09 & 229 & ETD\footnotemark{e} & $R$ & 57 & 180 & 2.11 \\ 
      & 2017 Oct 01 & 447 & Danish 1.54 m & $B$ &  224 & 30 &   3.48\\
\hline                  
\end{tabular}
\footnotetext{a}{The epoch 0 is $T_{0}$ in Tables , for WASP-18b, WASP-19b and WASP-77Ab, respectively.}
\footnotetext{b}{For the variable exposure times, we consider the average during the night.}
\footnotetext{c}{The RMS values were computed from the best fitted model of each light curve.}
\footnotetext{d}{Light curves obtained with only one reference star.}
\end{table*}

\begin{table}

\caption{Example photometry of WASP-18, WASP-19 and WASP-77A}
\label{examplephot}
\centering
\begin{tabular}{c c c c}
\hline \hline
Target & ${\rm BJD_{TDB}}$\footnotemark{a} & Relative flux & Error\\
\hline
    WASP-18b &  2457658.658241   & 1.00168 & 0.00078 \\
             &  2457658.660591   & 1.00138 & 0.00080 \\
             &  2457658.661771   & 1.00195 & 0.00082 \\
             &  2457658.662940   & 1.00261 & 0.00085 \\
             &  2457658.664109   & 1.00137 & 0.00086 \\\smallskip
      & ...           & ...         &    ... \\
    WASP-19b & 2457086.543926   & 1.00099 & 0.00086  \\
             & 2457086.544916   & 1.00173 & 0.00091  \\
             & 2457086.545905   & 1.00139 & 0.00086  \\
             & 2457086.546895   & 1.00045 & 0.00094  \\
             & 2457086.547886   & 1.00064 & 0.00093  \\\smallskip
     &  ...           & ...         &    ...  \\
WASP-77Ab & 2457299.78624 & 1.00229 & 0.00028 \\ 
         & 2457299.78764 & 1.00116 & 0.00022 \\
         & 2457299.78855 & 1.00201 & 0.00022 \\
         & 2457299.78946 & 1.00216 & 0.00022 \\
         & 2457299.79092 & 1.00133 & 0.00021 \\
         & ...           & ...         &    ... \\    
\hline
\end{tabular}
\footnotetext{These tables are available in machine-readable form.\\
\footnotetext{a}{The column time was converted to (${\rm BJD_{TDB}}$), following the procedure of \cite{Eastman2010}.}
}
\end{table}

@@

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{imagenes/light_curves2.pdf}
\caption{Light curves of WASP-18, WASP19 and WASP77 during 8, 9 and 9 different transits, respectively, from the TraMoS project. The fitted best model from EXOFASTv2 is shown as a light blue solid line for WASP-18b, orange for WASP-19b and pink for WASP-77Ab. To the right of each panel are the corresponding residuals of the model. For clarity, both light curves and their residual are offset artificially. The epoch number is indicated above each light curve. The technical information about each observation is listed in Table~\ref{log_table}.}
\label{transits}
\end{figure*}

\begin{figure*}
%\vspace{0.1cm}\hspace{0.2cm}
\includegraphics[width=1.0\textwidth]{imagenes/rv_all.pdf}
\caption{Radial velocity observations of WASP-18, WASP-19 and WASP-77A from \cite{Hellier2009}, \cite{Hebb2010} and \cite{Maxted2013}, respectively. The best fitted model from the joint modeling of RV and light curves with EXOFASTv2 is in solid line color: light blue for WASP-18b, orange for WASP-19b and pink for WASP-77Ab. The residuals of the model are shown at the bottom panel of each figure.}
\label{rv}
\end{figure*}

@@

\begin{landscape}
\begin{longtable}{llccc}
\caption{System parameter of WASP-18}
\label{wasp18}
\centering
\tabularnewline
\hline 
Parameter & Units & This work & \cite{Hellier2009} & \cite{Shporer2018} \\
\hline
\smallskip\\\multicolumn{2}{l}{Stellar Parameters:}&\smallskip\\
~~~~$M_*$  &Mass (\(M_\odot\))  &$1.294^{+0.063}_{-0.061}$ & $1.25\pm0.13$ &  \\
~~~~$R_*$  &Radius (\(R_\odot\))  &$1.319^{+0.061}_{-0.062}$ &$1.26^{+0.067}_{-0.054}$ & \\
~~~~$L_*$  &Luminosity (\(L_\odot\))  &$2.68^{+0.28}_{-0.26}$ & &\\
~~~~$\rho_*$  &Density (cgs)  &$0.795^{+0.11}_{-0.089}$ & $ 0.707^{+0.056}_{-0.096}$&\\
~~~~$\log{g}$  & Surface gravity (cgs)  &$4.310^{+0.036}_{-0.033}$ &$4.367^{+0.028}_{-0.042}$ & \\
~~~~$T_{\rm eff}$  &Effective Temperature (K)  &$6432\pm48$ & $6400\pm100$& \\
~~~~$[{\rm Fe/H}]$  &Metallicity   &$0.107\pm0.080$ & $0.00\pm0.09$ & \\
~~~~$Age$  &Age (Gyr)  &$1.57^{+1.4}_{-0.94}$ & $0.5-1.5$ & \\
%~~~~$d$  &Distance (pc)  &$122.2^{+9.9}_{-8.2}$ & $100\pm10$ & \\

\smallskip\\\multicolumn{2}{l}{Planetary Parameters:}&\smallskip\\
~~~~$R_P$  &Radius (\rj)  &$1.310\pm0.071$ & $1.106^{+0.072}_{-0.054}$& $1.192\pm0.038$\\
~~~~$M_P$  &Mass (\mj)  &$10.48^{+0.42}_{-0.40}$ & $10.30\pm0.69$ & \\
~~~~$P$  &Period (days)  &$0.94145236\pm(49)$ & $0.94145299\pm(87)$& $0.9414576^{(+34)}_{(-35)}$ \\
~~~~$e$  &Eccentricity   &$0.0061^{+0.0089}_{-0.0044}$ & &\\
~~~~$a$  &Semi-major axis (AU)  &$0.02054^{+0.00033}_{-0.00032}$ & $0.02045\pm0.00067$&\\
~~~~$\omega_*$  &Argument of Periastron (Degrees)  &$-100^{+110}_{-120}$ &  &\\
~~~~$\rho_P$  &Density (cgs)  &$5.79^{+0.97}_{-0.78}$& $7.73^{+0.78}_{-1.27}$\footnotemark{b} & \\
~~~~$logg_P$  &Surface gravity   &$4.180^{+0.044}_{-0.041}$ & $4.289^{+0.027}_{-0.050}$ &\\
~~~~$T_{eq}$  &Equilibrium temperature (K)  &$2485^{+53}_{-56}$ & $2384^{+58}_{-30}$ & \\
~~~~$\Theta$  &Safronov Number   &$0.254^{+0.015}_{-0.014}$ & &\\
~~~~$\fave$  &Incident Flux (\fluxcgs)  &$8.66^{+0.77}_{-0.75}$ & & \\

\smallskip\\\multicolumn{2}{l}{Primary Transit Parameters:}&\smallskip\\
~~~~$T_0$  &Transit time (\bjdtdb)  &$2456740.80560\pm(19)$ & $2454221.48163\pm(38)$ & $2458361.048072^{(+34)}_{(-35)}$\\
~~~~$i$  &Inclination (Degrees)  &$83.5^{+2.0}_{-1.6}$ & $86.0\pm2.5$ & $84.31^{+0.40}_{-0.37}$\\
~~~~$R_P/R_*$  &Radius of planet in stellar radii   &$0.1021\pm0.0011$ &  $0.0935\pm0.0011$ & $0.09721^{+0.00016}_{-0.00017}$\\
~~~~$a/R_*$  &Semi-major axis in stellar radii   &$3.35^{+0.15}_{-0.13}$ & & $3.523^{+0.028}_{-0.027}$\\
~~~~$b$  &Impact parameter   &$0.433^{+0.07}_{-0.10}$ & $0.25\pm0.15$ & $0.349^{+0.020}_{-0.022}$\\
~~~~$\delta$  &Transit depth (fraction)  &$0.01041\pm0.00022$ & & $0.009449^{+0.000032}_{-0.000032}$\\
~~~~$u_{1,I}$  &linear LD coeff., I band  &$0.207\pm0.019$ & &\\
~~~~$u_{2,I}$  &quadratic LD coeff., I band  &$0.313\pm0.019$& &\\
~~~~$u_{1,R}$  &linear LD coeff., R band  & $0.257\pm0.045$ & &\\
~~~~$u_{2,R}$  &quadratic LD coeff., R band  &$0.309\pm0.048$ & &\\
~~~~$T_{14}$  &Total transit duration (days)  &$0.0931^{+0.0011}_{-0.0010}$ & $0.08932\pm0.00068$ &\\
~~~~$P_T$  &A priori non-grazing transit prob   &$0.268^{+0.011}_{-0.012}$ & &\\
~~~~$P_{T,G}$  &A priori transit prob   &$0.328^{+0.014}_{-0.015}$ & &\\
~~~~$\tau$  &Ingress/egress transit duration (days)  &$0.0107\pm0.0010$ & &\\

\smallskip\\\multicolumn{2}{l}{RV Parameters:}&\smallskip\\
~~~~$ecos{\omega_*}$  &   &$-0.0004^{+0.0038}_{-0.0045}$ & &\\
~~~~$esin{\omega_*}$  &   &$-0.0008^{+0.0056}_{-0.0092}$ & &\\
~~~~$K$  &RV semi-amplitude (m/s)  &$1807^{+34}_{-36}$ & $1818.3\pm8.0$ &\\
~~~~$M_P\sin i$  &Minimum mass (\mj)  &$10.40\pm0.40$ & &\\
\smallskip\\\multicolumn{2}{l}{Secondary Eclipse Parameters:}&\smallskip\\
~~~~$T_S$  &Time of eclipse (\bjdtdb)  &$2457657.3076^{+0.0023}_{-0.0027}$ & &\\
~~~~$b_S$  &Eclipse impact parameter   &$0.431^{+0.070}_{-0.100}$ & &\\
~~~~$\tau_S$  &Ingress/egress eclipse duration (days)  &$0.0106^{+0.0011}_{-0.0010}$ & &\\
~~~~$T_{S,14}$  &Total eclipse duration (days)  &$0.0929\pm0.0017$ & &\\
~~~~$P_S$  &A priori non-grazing eclipse prob   &$0.269^{+0.010}_{-0.011}$ & &\\
~~~~$P_{S,G}$  &A priori eclipse prob   &$0.330^{+0.013}_{-0.014}$ & &\\
\hline 
\end{longtable}
\end{landscape}
%\tablefoot{
%\tablefoottext{a}{Value converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.}
%\tablefoottext{b}{Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.}
%\tablefoottext{c}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}}

@@

 A transit timing variation is represented trough a difference in time from the transit mid-time $T_c$, for a planet in Keplerian motion following a linear ephemeris of the orbital period. The TTVs were computed considering our transit times from the TraMoS project, as well as including previous published ones. A refined orbital period was linearly fitted, considering 19, 59 and 11 transit times of WASP-18b, WASP-19b, and WASP-77Ab, respectively. Along the linear fit, we also tested a second degree polynomial fit to analyze a possible orbital decay. Both fit considered the errors of the data. In Figures~\ref{wasp18_ttv}, \ref{wasp19_ttv}, and XXX, are presented all the TTV values for the transit times of WASP-18b, WASP-19b and WASP-77Ab, respectively.

@@

@@

Shown in Figure~\ref{wasp18_ttv} is the linear plot of TTV versus epoch for this planet. The deviations of the transit times from the linear ephemeris has an RMS of 83 seconds. The greater deviations come from the transit time of the epochs $-1904$ and $-1184$, which are over the linear ephemeris by $2.5\sigma$ and $1.9\sigma$, respectively. If those values are removed, the RMS decreases to 61 seconds. Considering all the transit times in Table~\ref{times_wasp18} without the epochs $-1904$ and $-1184$, all the TTVs lie within $1.6\sigma$ in the linear fit.

@@

\begin{figure*}
%\vspace{0.1cm}\hspace{0.2cm}
\includegraphics[width=1.0\textwidth]{imagenes/WASP18_TTV.png}
\caption{Observed minus calculated mid-transit times (TTV) for WASP-18b. The dashed black line corresponds to the proposed linear ephemeris, i.e. zero deviation from the predicted transit time  computed from our refined orbital period. For that, we considered 63 transit times from the TraMoS project (in light blue), published works and TESS (both in black). The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.  The RMS scatter from the linear ephemeris is 47 seconds.}
\label{wasp18_ttv}
\end{figure*}

@@

Figure~\ref{wasp19_ttv} shows the TTV values versus epoch, for all the transit time considered in this work.

@@

\begin{figure*}
%\vspace{0.1cm}\hspace{0.2cm}
\includegraphics[width=1.0\textwidth]{imagenes/WASP19_TTV.png}
\caption{Observed minus calculated mid-transit times (TTV) for WASP-19b. The dashed black line corresponds to the proposed linear ephemeris, i.e. zero deviation from the predicted transit time  computed from our refined orbital period. For that, we considered 87 transit times from the TraMoS project (in light blue), published works and TESS (both in black). The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.  The RMS scatter from the linear ephemeris is 65 seconds.}
\label{wasp19_ttv}
\end{figure*}

>>>>

\chapterauthor{P\'ia Cort\'es-Zuleta$^{1,2}$, Patricio Rojo$^{1}$, Songhu Wang$^{2,5}$, Tobias C. Hinse$^{3}$, Sergio Hoyer$^{4}$, Bastian Sanhueza$^{1}$, Patricio Correa-Amaro$^{1}$, Julio Albornoz$^{1}$}

\begin{flushleft}
\vspace{-1cm}
$^{1}$ Departamento de Astronom\'ia, Universidad de Chile, Camino El Observatorio 1515, Las Condes, Santiago, Chile \\
$^{2}$ Department of Astronomy, Yale University, New Haven, CT 06511, USA \\
$^{3}$ Chungnam National University, Department of Astronomy and Space Science, 34134 Daejeon, Republic of Korea \\ 
$^{4}$ Aix Marseille Univ, CNRS, CNES, LAM, Marseille, France \\
$^{5}$ \emph{51 Pegasi b} Fellow \\
\end{flushleft}

@@

\begin{table}
\caption{Log of Observations}             
\label{log_table}      
\centering          
\begin{threeparttable}
\begin{tabular}{cccccccc}
\hline\hline       
Target & Date & Epoch\tnote{a} & Telescope & Filter & N & $t_{exp}$\tnote{b} & RMS\tnote{c} \\
& (UTC) &       &           &       &                   & (seconds) & (mmag)\\
\hline  
WASP-18 & 2009 Oct 28 &-1904 & SMARTS 1 m & $I$ & 1412 & 1.5 & 8.49  \\
 				& 2009 Oct 29 & -1903 & SMARTS 1 m & $I$ & 1435 & 2 & 5.67 \\
				& 2009 Oct 30 & -1902 & SMARTS 1 m & $I$ & 1198 & 2  & 4.50 \\
 				& 2011 Sep 06 & -1184 & SMARTS 1 m & $I$ & 203 & 15 & 2.40 \\
				& 2016 Sep 24\tnote{d} & 776 & Danish 1.54 m & $I$ & 138 & 90 & 1.05  \\
				& 2016 Sep 25\tnote{d} & 777 &Danish 1.54 m & $I$ & 159 & 90  & 0.96  \\
			    & 2016 Sep 26\tnote{d} & 778 & Danish 1.54 m & $I$ & 113 & 90 & 0.87  \\ \smallskip
				& 2017 Sep 29\tnote{d} & 1169 & Danish 1.54 m & $R$ & 330 & 30 & 2.53 \\
WASP-19 & 2011 Apr 22 & -923 & SMARTS 1 m &   $I$ &  626  & 12  & 4.31   \\
     & 2011 Dec 24 & -611 & SMARTS 1 m &   $I$ & 364  & 18  & 35.9 \\
     & 2013 Mar 13 & -47 & Danish 1.54 m & $R$ & 336 & 35 & 2.15\\
     & 2013 Apr 20 & 1 & Danish 1.54 m & $R$ & 153 & 100 & 0.80 \\
     & 2015 Mar 04 & 867 & Danish 1.54 m & $R$ & 235 & 60 & 0.84\\
     & 2016 Apr 14 & 1383 & Danish 1.54 m & $I$ & 87 & 100 & 0.71\\
     & 2017 Feb 14 & 1771 & Danish 1.54 m & $I$ & 137 & 90 & 0.79\\
     & 2017 Apr 08 & 1838 & Danish 1.54 m & $R$ & 125 & 90 & 0.81\\\smallskip
     & 2017 Oct 03 & 2064 & Danish 1.54 m & $R$ & 43 & 110 & 1.70\\ 
 WASP-77 & 2013 Aug 20 & -659 & ETD\tnote{e} & $clear$ & 103 & 120 & 3.87  \\
    & 2013 Oct 30 & -606 & ETD\tnote{e} & $clear$ & 690 & 12 & 5.91 \\
    & 2015 Sep 29 & -92 & Danish 1.54 m & $R$ &  244 & 30 &  0.84\\
      & 2015 Oct 03 & -89 & Danish 1.54 m & $R$ &  138 & 60 &  1.84\\
      & 2016 Sep 26 & 175 & Danish 1.54 m & $I$ &  90 & 90 &  0.47\\
      & 2016 Sep 30 & 177 & ETD\tnote{e}& $clear$ & 66 & 180 & 2.74 \\
      & 2016 Oct 07 & 183 & Warsaw 1.3 m & $I$ & 237 & 60 &  2.38 \\ 
      & 2016 Dec 09 & 229 & ETD\tnote{e} & $R$ & 57 & 180 & 2.11 \\ 
      & 2017 Oct 01 & 447 & Danish 1.54 m & $B$ &  224 & 30 &   3.48\\
\hline                  
\end{tabular}
\begin{tablenotes}
	\footnotesize
	\item[a] The epoch 0 is $T_{0}$ in Tables \ref{wasp18},\ref{tab:wasp19} and \ref{tab:wasp77}, for WASP-18b, WASP-19b and WASP-77Ab, respectively.
	\item[b] For the variable exposure times, we consider the average during the night.
	\item[c] RMS values were computed from the best fitted model of each light curve.
	\item[d] Light curves obtained with only one reference star.
	\item[e] These light curves were obtained from the Exoplanet Transit Database (ETD) \url{var2.astro.cz/ETD}.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\begin{table}[ht]
\caption{Example photometry of WASP-18, WASP-19 and WASP-77A}
\label{examplephot}
\centering
\begin{threeparttable}
\begin{tabular}{c c c c}
\hline \hline
Target & ${\rm BJD_{TDB}}$\tnote{a} & Relative flux & Error\\
\hline
    WASP-18b &  2457658.658241   & 1.00168 & 0.00078 \\
             &  2457658.660591   & 1.00138 & 0.00080 \\
             &  2457658.661771   & 1.00195 & 0.00082 \\
             &  2457658.662940   & 1.00261 & 0.00085 \\
             &  2457658.664109   & 1.00137 & 0.00086 \\\smallskip
      & ...           & ...         &    ... \\
    WASP-19b & 2457086.543926   & 1.00099 & 0.00086  \\
             & 2457086.544916   & 1.00173 & 0.00091  \\
             & 2457086.545905   & 1.00139 & 0.00086  \\
             & 2457086.546895   & 1.00045 & 0.00094  \\
             & 2457086.547886   & 1.00064 & 0.00093  \\\smallskip
     &  ...           & ...         &    ...  \\
WASP-77Ab & 2457299.78624 & 1.00229 & 0.00028 \\ 
         & 2457299.78764 & 1.00116 & 0.00022 \\
         & 2457299.78855 & 1.00201 & 0.00022 \\
         & 2457299.78946 & 1.00216 & 0.00022 \\
         & 2457299.79092 & 1.00133 & 0.00021 \\
         & ...           & ...         &    ... \\    
\hline
\end{tabular}
\begin{tablenotes}
\item These tables are available in machine-readable form.
\item[a]The column time was converted to (${\rm BJD_{TDB}}$), following the procedure of \cite{Eastman2010}.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{imagenes/light_curves2.pdf}
\caption{Light curves of WASP-18, WASP19 and WASP77 during 8, 9 and 9 different transits, respectively, from the TraMoS project. The fitted best model from EXOFASTv2 is shown as a light blue solid line for WASP-18b, orange for WASP-19b and pink for WASP-77Ab. To the right of each panel are the corresponding residuals of the model. For clarity, both light curves and their residual are offset artificially. The epoch number is indicated above each light curve. The technical information about each observation is listed in Table~\ref{log_table}.}
\label{transits}
\end{figure}

\begin{figure}
%\vspace{0.1cm}\hspace{0.2cm}
\includegraphics[width=1.0\textwidth]{imagenes/rv_all.pdf}
\caption{Radial velocity observations of WASP-18, WASP-19 and WASP-77A from \cite{Hellier2009}, \cite{Hebb2010} and \cite{Maxted2013}, respectively. The best fitted model from the joint modeling of RV and light curves with EXOFASTv2 is in solid line color: light blue for WASP-18b, orange for WASP-19b and pink for WASP-77Ab. The residuals of the model are shown at the bottom panel of each figure.}
\label{rv}
\end{figure}

@@

\begin{landscape}
\begin{ThreePartTable}
\begin{TableNotes}
\item Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.
\item[a] Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.
\end{TableNotes}
\begin{longtable}{llccc}
\caption{System parameter of WASP-18}
\label{wasp18}
\centering
\tabularnewline
\hline 
Parameter & Units & This work & \cite{Hellier2009} & \cite{Shporer2018} \\
\hline
\smallskip\\\multicolumn{2}{l}{Stellar Parameters:}&\smallskip\\
~~~~$M_*$\dotfill &Mass (\(M_\odot\))\dotfill &$1.294^{+0.063}_{-0.061}$ & $1.25\pm0.13$ &  \\
~~~~$R_*$\dotfill &Radius (\(R_\odot\))\dotfill &$1.319^{+0.061}_{-0.062}$ &$1.26^{+0.067}_{-0.054}$ & \\
~~~~$L_*$\dotfill &Luminosity (\(L_\odot\))\dotfill &$2.68^{+0.28}_{-0.26}$ & &\\
~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$0.795^{+0.11}_{-0.089}$ & $ 0.707^{+0.056}_{-0.096}$&\\
~~~~$\log{g}$\dotfill & Surface gravity (cgs)\dotfill &$4.310^{+0.036}_{-0.033}$ &$4.367^{+0.028}_{-0.042}$ & \\
~~~~$T_{\rm eff}$\dotfill &Effective Temperature (K)\dotfill &$6432\pm48$ & $6400\pm100$& \\
~~~~$[{\rm Fe/H}]$\dotfill &Metallicity \dotfill &$0.107\pm0.080$ & $0.00\pm0.09$ & \\
~~~~$Age$\dotfill &Age (Gyr)\dotfill &$1.57^{+1.4}_{-0.94}$ & $0.5-1.5$ & \\
%~~~~$d$\dotfill &Distance (pc)\dotfill &$122.2^{+9.9}_{-8.2}$ & $100\pm10$ & \\

\smallskip\\\multicolumn{2}{l}{Planetary Parameters:}&\smallskip\\
~~~~$R_P$\dotfill &Radius (\rj)\dotfill &$1.310\pm0.071$ & $1.106^{+0.072}_{-0.054}$& $1.192\pm0.038$\\
~~~~$M_P$\dotfill &Mass (\mj)\dotfill &$10.48^{+0.42}_{-0.40}$ & $10.30\pm0.69$ & \\
~~~~$P$\dotfill &Period (days)\dotfill &$0.94145236\pm(49)$ & $0.94145299\pm(87)$& $0.9414576^{(+34)}_{(-35)}$ \\
~~~~$e$\dotfill &Eccentricity \dotfill &$0.0061^{+0.0089}_{-0.0044}$ & &\\
~~~~$a$\dotfill &Semi-major axis (AU)\dotfill &$0.02054^{+0.00033}_{-0.00032}$ & $0.02045\pm0.00067$&\\
~~~~$\omega_*$\dotfill &Argument of Periastron (Degrees)\dotfill &$-100^{+110}_{-120}$ &  &\\
~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$5.79^{+0.97}_{-0.78}$& $7.73^{+0.78}_{-1.27}$\tnote{a} & \\
~~~~$logg_P$\dotfill &Surface gravity \dotfill &$4.180^{+0.044}_{-0.041}$ & $4.289^{+0.027}_{-0.050}$ &\\
~~~~$T_{eq}$\dotfill &Equilibrium temperature (K)\dotfill &$2485^{+53}_{-56}$ & $2384^{+58}_{-30}$ & \\
~~~~$\Theta$\dotfill &Safronov Number \dotfill &$0.254^{+0.015}_{-0.014}$ & &\\
~~~~$\fave$\dotfill &Incident Flux (\fluxcgs)\dotfill &$8.66^{+0.77}_{-0.75}$ & & \\

\smallskip\\\multicolumn{2}{l}{Primary Transit Parameters:}&\smallskip\\
~~~~$T_0$\dotfill &Transit time (\bjdtdb)\dotfill &$2456740.80560\pm(19)$ & $2454221.48163\pm(38)$ & $2458361.048072^{(+34)}_{(-35)}$\\
~~~~$i$\dotfill &Inclination (Degrees)\dotfill &$83.5^{+2.0}_{-1.6}$ & $86.0\pm2.5$ & $84.31^{+0.40}_{-0.37}$\\
~~~~$R_P/R_*$\dotfill &Radius of planet in stellar radii \dotfill &$0.1021\pm0.0011$ &  $0.0935\pm0.0011$ & $0.09721^{+0.00016}_{-0.00017}$\\
~~~~$a/R_*$\dotfill &Semi-major axis in stellar radii \dotfill &$3.35^{+0.15}_{-0.13}$ & & $3.523^{+0.028}_{-0.027}$\\
~~~~$b$\dotfill &Impact parameter \dotfill &$0.433^{+0.07}_{-0.10}$ & $0.25\pm0.15$ & $0.349^{+0.020}_{-0.022}$\\
~~~~$\delta$\dotfill &Transit depth (fraction)\dotfill &$0.01041\pm0.00022$ & & $0.009449^{+0.000032}_{-0.000032}$\\
~~~~$u_{1,I}$\dotfill &linear LD coeff., I band\dotfill &$0.207\pm0.019$ & &\\
~~~~$u_{2,I}$\dotfill &quadratic LD coeff., I band\dotfill &$0.313\pm0.019$& &\\
~~~~$u_{1,R}$\dotfill &linear LD coeff., R band\dotfill & $0.257\pm0.045$ & &\\
~~~~$u_{2,R}$\dotfill &quadratic LD coeff., R band\dotfill &$0.309\pm0.048$ & &\\
~~~~$T_{14}$\dotfill &Total transit duration (days)\dotfill &$0.0931^{+0.0011}_{-0.0010}$ & $0.08932\pm0.00068$ &\\
~~~~$P_T$\dotfill &A priori non-grazing transit prob \dotfill &$0.268^{+0.011}_{-0.012}$ & &\\
~~~~$P_{T,G}$\dotfill &A priori transit prob \dotfill &$0.328^{+0.014}_{-0.015}$ & &\\
~~~~$\tau$\dotfill &Ingress/egress transit duration (days)\dotfill &$0.0107\pm0.0010$ & &\\

\smallskip\\\multicolumn{2}{l}{RV Parameters:}&\smallskip\\
~~~~$e\cos{\omega_*}$\dotfill & \dotfill &$-0.0004^{+0.0038}_{-0.0045}$ & &\\
~~~~$e\sin{\omega_*}$\dotfill & \dotfill &$-0.0008^{+0.0056}_{-0.0092}$ & &\\
~~~~$K$\dotfill &RV semi-amplitude (m/s)\dotfill &$1807^{+34}_{-36}$ & $1818.3\pm8.0$ &\\
~~~~$M_P\sin i$\dotfill &Minimum mass (\mj)\dotfill &$10.40\pm0.40$ & &\\
\smallskip\\\multicolumn{2}{l}{Secondary Eclipse Parameters:}&\smallskip\\
~~~~$T_S$\dotfill &Time of eclipse (\bjdtdb)\dotfill &$2457657.3076^{+0.0023}_{-0.0027}$ & &\\
~~~~$b_S$\dotfill &Eclipse impact parameter \dotfill &$0.431^{+0.070}_{-0.100}$ & &\\
~~~~$\tau_S$\dotfill &Ingress/egress eclipse duration (days)\dotfill &$0.0106^{+0.0011}_{-0.0010}$ & &\\
~~~~$T_{S,14}$\dotfill &Total eclipse duration (days)\dotfill &$0.0929\pm0.0017$ & &\\
~~~~$P_S$\dotfill &A priori non-grazing eclipse prob \dotfill &$0.269^{+0.010}_{-0.011}$ & &\\
~~~~$P_{S,G}$\dotfill &A priori eclipse prob \dotfill &$0.330^{+0.013}_{-0.014}$ & &\\
\hline
\insertTableNotes \\
\end{longtable}
\end{ThreePartTable}
\end{landscape}
%\tablefoot{
%\tablefoottext{a}{Value converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.}
%\tablefoottext{b}{Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.}
%\tablefoottext{c}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}}

@@

 A transit timing variation is represented trough a difference in time from the transit mid-time $T_c$, for a planet in Keplerian motion following a linear ephemeris of the orbital period. The TTVs were computed considering our transit times from the TraMoS project, as well as including previous published ones. A refined orbital period was linearly fitted, considering 19, 59 and 11 transit times of WASP-18b, WASP-19b, and WASP-77Ab, respectively. Along the linear fit, we also tested a second degree polynomial fit to analyze a possible orbital decay. Both fit considered the errors of the data. In Figure \ref{all_ttv} are presented all the TTV values for the transit times of WASP-18b, WASP-19b and WASP-77Ab, respectively.

@@

\begin{figure}
\centering
\includegraphics[width=1.0\columnwidth]{imagenes/TTVs.png}
\caption{Observed minus calculated mid-transit times (TTV) for WASP-18b (top), WASP-19b (center) and WASP-77Ab (bottom). The dashed black line corresponds to the proposed linear ephemeris, i.e. zero deviation from the predicted transit time (See Section \ref{ttvsection}) computed from our refined orbital period. For that, we considered 19, 59 and 11 transit times of WASP-18b, WASP-19b, and WASP-77Ab, respectively. The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal. The points in color are the TTV from the newly light curves of the TraMoS project (WASP-18b: light blue, WASP-19b: orange, WASP-77Ab: pink) and the black points in the three panels are TTVs measured from previous published transit times. The RMS scatter from the linear ephemeris are 83 seconds for WASP-18b; 75 seconds for WASP-19b, and 121 seconds for WASP-77Ab.}
\label{all_ttv}
\end{figure}

@@

The top panel of Figure~\ref{all_ttv} is the linear plot of TTV versus epoch for this planet. The deviations of the transit times from the linear ephemeris has an RMS of 83 seconds. The greater deviations come from the transit time of the epochs $-1904$ and $-1184$, which are over the linear ephemeris by $2.5\sigma$ and $1.9\sigma$, respectively. If those values are removed, the RMS decreases to 61 seconds. Considering all the transit times in Table~\ref{times_wasp18} without the epochs $-1904$ and $-1184$, all the TTVs lie within $1.6\sigma$ in the linear fit.

@@

@@

At the middle panel of Figure~\ref{all_ttv} are the TTV values versus epoch, for all the transit time considered in this work.

@@
